---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# usbtc08r

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/usbtc08r)](https://CRAN.R-project.org/package=usbtc08r)
[![R-CMD-check](https://github.com/royratcliffe/usbtc08r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/royratcliffe/usbtc08r/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of usbtc08r is to ...

## Installation

You can install the development version of `usbtc08r` as follows, starting with `devtools` if not already installed:

``` r
install.packages("devtools")
remotes::install_github("royratcliffe/usbtc08r", "royratcliffe-patch-3")
```

Before installation can succeed, you first need to install Pico Technology's `libusbtc08` driver library. Install the PicoSDK on Windows, or on macOS, but install using Aptitude as package `libusbtc08-dev` on Linux. The build process needs access to the driver's header and shared library.

### Rtools on Windows

You need [Rtools](https://cran.r-project.org/bin/windows/Rtools/) to build the package on Windows. The package includes C++, so needs the compiler toolchain. Check for package build problems using the `pkgbuild` package.
```{r eval=FALSE}
pkgbuild::check_build_tools(debug = TRUE)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE, include=TRUE}
library(usbtc08r)
## basic example code
```

## Unit Behaviour, Synchronous and Asynchronous

Each unit comprises nine channels. Strictly speaking, using Unified Modelling nomenclature, units _compose_ of channels; the life time of the channel strictly depends on its unit. Units "have" channels, the [stronger form of aggregation](https://www.uml-diagrams.org/composition.html).

Units have two modes of operation: synchronous and asynchronous. The difference between these modes extends beyond the driver threading model. A unit itself switches mode accordingly and precludes behaviours from the non-operating mode. Specifically, asking for a single sample set fails when running asynchronously. Software experimentation quickly discovers this limitation, or feature, which impacts driver acquisition design.

Asynchronous mode switches the unit into a more advanced form of temperature data collection where the Pico Technology firmware records time-stamped temperature readings for all its enabled channels. By implication, therefore, channel set-up always precedes acquisition; nor can set-up interlace with asynchronous running. Switching thermocouple types requires a shut-down and re-start.

## References

* [libusbtc08-1&mdash;Hardware interface library for PicoTech USB TC08 Thermocouple sensor](https://reposcope.com/package/libusbtc08-1)
* [Linux Software & Drivers for Oscilloscopes and Data Loggers](https://www.picotech.com/downloads/linux)
* [Pico Technology at GitHub](https://github.com/picotech)
* [TC-08 thermocouple data logger](https://www.picotech.com/data-logger/tc-08/thermocouple-data-logger)
* [Pico SDK C examples at GitHub](https://github.com/picotech/picosdk-c-examples/tree/master/usbtc08)
* [USB TC-08 Thermocouple Data Logger MATLAB Examples](https://github.com/picotech/picosdk-usbtc08-matlab-examples)
