---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# usbtc08r

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/usbtc08r)](https://CRAN.R-project.org/package=usbtc08r)
[![R-CMD-check](https://github.com/royratcliffe/usbtc08r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/royratcliffe/usbtc08r/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of usbtc08r is to ...

## Installation

You can install the development version of `usbtc08r` like so, starting with `devtools` if not already installed:

``` r
install.packages("devtools")
remotes::install_github("royratcliffe/usbtc08r", "royratcliffe-patch-3")
```

Before installation can succeed, you first need to install Pico Technology's `libusbtc08` driver library. Install the PicoSDK on Windows, or on macOS, but install using Aptitude as package `libusbtc08-dev` on Linux. The build process needs access to the driver's header and shared library.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(usbtc08r)
## basic example code
```
