---
title: "Redis Stack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Redis Stack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(usbtc08r)
```

## Docker container stack

### Redis and Redis Insight stack
Publishes ports 6379 and 8001 respectively. Read [more about Redis Insight](https://docs.redis.com/latest/ri/).

### `pico-tc08` service
1. Based on `rocker/r-ver` version 4 or above.
2. Requires privileged for access to USB-connected thermocouple device, or devices. Supports multiple devices of nine channels each.
3. Container requires additional development libraries: `libusbtc08-dev` and `libhiredis-dev`.

The container requires `remotes` explicitly. The `littler` scripts, specifically the GitHub installer, does _not_ install `remotes` automatically; rather, it presumes preinstalled. Tempting to remove the development packages for `libusbtc08` and `libhiredis` since no longer required after compilation. However, auto-remove will remove the shared-library packages; these _are_ required by the streaming process run-time.
